Out-of-Sample Comparisons of Overfit Models

### 2016-01-23 paper.tex
[#36] Clarify that we use *strict* stationarity in Assumption 1
One of the referees found the statement of "stationarity" without any
modification a bit confusing and initially assumed *weak* stationarity.
This commit removes that confusion.

\begin{asmp}\label{asmp-1}
  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
  greater than two and discussed further in Assumption \ref{asmp-3}.
\end{asmp}

>>>>

\begin{asmp}\label{asmp-1}
  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
  greater than two and discussed further in Assumption \ref{asmp-3}.
\end{asmp}
